Ensemble Methods for Robust Feature Selection

### 2016-08-02 paper/paper.tex
removed merge comments

The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left. In the experiments, $10\%$ of the size of all features were discarded at each step. The procedure was repeated until a subset of the size of $1\%$ of all features was left. Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps. Therefore a SVM is $10$ times needed to be evaluated. Another method would be to discard only $10\%$ of the remaining features. A more gradually ascend of feature weights can be achievedthis way. However this was not computable with our ressources. For the hpyerparameter $C$ a grid search on the set $/{1, 10, 100, 1000\}$ was done. The parameters were evaluated with stratisfied 5-fold cross-validation.

@@

\subsection{Results}
- Do SVM\_RFE with exponential rising
- SU achieved high values in the paper, in our results SU weighted a lot of features the 
same; therefore for robustness same weights have to be shuffled to not accidental increase
robustness by order of features
- The noise features of the NIPS 2003 challenge data sets are highly correlated with the
real feature; therefore no improvement has been made with feature selection in terms of 
accuracy
% Acknowledgements should go at the end, before appendices and references

>>>>

The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left. In the experiments, $10\%$ of the size of all features were discarded at each step. The procedure was repeated until a subset of the size of $1\%$ of all features was left. Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps. Therefore a SVM is $10$ times needed to be evaluated. Another method would be to discard only $10\%$ of the remaining features. A more gradually ascend of feature weights can be achievedthis way. However this was not computable with our ressources. For the hpyerparameter $C$ a grid search on the set $\{1, 10, 100, 1000\}$ was done. The parameters were evaluated with stratisfied 5-fold cross-validation.

@@

\subsection{Results}
- SU achieved high values in the paper, in our results SU weighted a lot of features the 
same; therefore for robustness same weights have to be shuffled to not accidental increase
robustness by order of features

% Acknowledgements should go at the end, before appendices and references
